Bayesian Sparsification Methods for Deep Complex-valued Networks

### 2020-11-09 paper/paper.tex
typo fixes

% VD is a Bayesian perspective on dropout regularization \citep{hinton_improving_2012} offered
% by \citet{kingma_variational_2015} and repurposed for sparsification by \citet{molchanov_variational_2017}.
%
\citet{kingma_variational_2015} provided a unifying perspective on Dropout, DropConnect
\citep{wan_regularization_2013}, and Gaussian Dropout \citep{wang_fast_2013} through
the lens of Variational Inference and propose \emph{Variational Dropout}. They argued
that the multiplicative noise introduced by Dropout methods induces a distribution
equivalent to a fully factorized variational posterior $
  q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \eta_j$ with $
  \eta_j \sim p_\theta(\eta_j)
$ iid from some $p_\theta(\eta)$.
%
% Binary dropout with rate $p \in (0, 1)$ uses $
%   p_\eta
%     = \mathcal{B}\bigl(
%       \{0, \tfrac1{1-p}\}, 1-p
%     \bigr)
% $, whereas in Gaussian dropout $
%   \eta \sim \mathcal{N}(1, \alpha)
% $ for $\alpha = \tfrac{p}{1-p}$.
% This suggests making $\alpha$ a variational parameter
% and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,

@@

% why is there such a dramamtic difference in impact of ``fine-tune''?
We provide the following interpretation of the apparent contrast in performance impact
borne by fine-tuning between less than $\times50$ and higher than $\times100$ compression
regimes in figure~\ref{fig:musicnet__trade-off}, also observed in sec.~\ref{sub:mnist_like_datasets}.
%
% * early stopping kick in at around 10-20 epoch
% * performance peaks at 10-15 epoch and then gradually declines
The value of $C$ in \eqref{eq:elbo_with_coef} is a good proxy for the ranking of the
final compression rate since it directly affects the feedback from sparsifying prior.
So, during the $50$ epoch allotted for ``sparsify'' stage, low $C$ prevents the sparsity
inducing prior from pulling the posterior sufficiently away from the likelihood-maximizing
parameters inherited from the ``pre-train'' stage. It is reasonable, therefore, to expect
that for undercompressed models the fine-tuning stage acts essentially as a continuation
of pre-training. And, since we have observed that longer training invariably deteriorates
the validation performance, the ``fine-tune'' stage should lead to overfitting for small
$C$.
%
Figure~\ref{fig:musicnet__early_stopping} shows that the models, which have been sparsified
with $C$ less than $\tfrac1{400}$, have less than $50\times$ compression and need considerably
less training epochs before early stopping terminates the process.

>>>>

% VD is a Bayesian perspective on dropout regularization \citep{hinton_improving_2012} offered
% by \citet{kingma_variational_2015} and repurposed for sparsification by \citet{molchanov_variational_2017}.
%
\citet{kingma_variational_2015} provided a unifying perspective on Dropout, DropConnect
\citep{wan_regularization_2013}, and Gaussian Dropout \citep{wang_fast_2013} through
the lens of Variational Inference and proposed \emph{Variational Dropout}. They argued
that the multiplicative noise introduced by Dropout methods induces a distribution
equivalent to a fully factorized variational posterior $
  q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \eta_j$ with $
  \eta_j \sim p_\theta(\eta_j)
$ iid from some $p_\theta(\eta)$.
%
% Binary dropout with rate $p \in (0, 1)$ uses $
%   p_\eta
%     = \mathcal{B}\bigl(
%       \{0, \tfrac1{1-p}\}, 1-p
%     \bigr)
% $, whereas in Gaussian dropout $
%   \eta \sim \mathcal{N}(1, \alpha)
% $ for $\alpha = \tfrac{p}{1-p}$.
% This suggests making $\alpha$ a variational parameter
% and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,

@@

% why is there such a dramamtic difference in impact of ``fine-tune''?
We provide the following interpretation of the apparent contrast in performance impact
borne by fine-tuning between less than $\times50$ and higher than $\times100$ compression
regimes in figure~\ref{fig:musicnet__trade-off}, also observed in sec.~\ref{sub:mnist_like_datasets}.
%
% * early stopping kick in at around 10-20 epoch
% * performance peaks at 10-15 epoch and then gradually declines
The value of $C$ in \eqref{eq:elbo_with_coef} is a good proxy for the ranking of the
final compression rate since it directly affects the feedback from sparsifying prior.
So, during the $50$ epochs allotted for ``sparsify'' stage, low $C$ prevents the sparsity
inducing prior from pulling the posterior sufficiently away from the likelihood-maximizing
parameters inherited from the ``pre-train'' stage. It is reasonable, therefore, to expect
that for undercompressed models the fine-tuning stage acts essentially as a continuation
of pre-training. And, since we have observed that longer training invariably deteriorates
the validation performance, the ``fine-tune'' stage should lead to overfitting for small
$C$.
%
Figure~\ref{fig:musicnet__early_stopping} shows that the models, which have been sparsified
with $C$ less than $\tfrac1{400}$, have less than $50\times$ compression and need considerably
less training epochs before early stopping terminates the process.
